Surrogate Modelling of the Tritium Breeding Ratio

### 2020-06-20 talk_ucl_cdt_200622/introduction.tex
shorten methodology slide

			\begin{itemize}
				\item
					Regression performance (capability to approximate)
					\begin{itemize}
						\item Absolute: mean absolute error, $\sigma$ of error
						\item Relative: $R^2$, $R^2_\text{adj.}$
					\end{itemize}
				\item
					Computational complexity:
					wall training \& prediction time / sample.
			\end{itemize}

			2 approaches for surrogate training:
			\begin{enumerate}
				\item
					Decoupled -- trains models from previously sampled
					$\mathcal{T}=\{(x,f(x))\}$.
				\item
					Adaptive -- repeats sampling \& model training, increases
					sampling density in low-performance regions.
			\end{enumerate}
\end{frame}

>>>>

			\begin{itemize}
				\item
					Regression performance: mean absolute error, $\sigma$ of
					error, $R^2$, $R^2_\text{adj.}$
				\item
					Computational complexity:
					wall training \& prediction time / sample.
			\end{itemize}

			2 approaches for surrogate training:
			\begin{enumerate}
				\item
					Decoupled -- trains models from previously sampled
					datapoints.
				\item
					Adaptive -- repeats sampling \& model training, increases
					sampling density in low-performance regions.
			\end{enumerate}
\end{frame}
